The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-04-09 exp-resurgence.tex
general updates and revisions

In Sections \ref{sec:geometry_laplace} and \ref{sec:geometry_borel}, we introduce a geometric picture of the Laplace and Borel transforms, generalizing the position domain from the complex plane to a translation surface $B$. Each translation chart $\zeta$ gives a different version of the Laplace transform, whose associated frequency domain is the cotangent space $T^*_{\zeta = 0} B$. The frequency coordinate $z$ is a canonical coordinate on $T^*_{\zeta = 0}B$, or on $T^*_{\zeta = 0}B^{\otimes n}$ if $\zeta = 0$ is a singularity with cone angle $2\pi n$.
\begin{center}
\phaseSpaceLaplace
\captionof{figure}{The frequency coordinate $z$ on the cotangent spaces of an ordinary point and a singular point. The singularity shown here has cone angle $6\pi$, like the singularities of the translation surface associated with the Airy function.}
\end{center}
%
\paragraph{New and old examples}
%
We illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}). \begin{todo}the anharmonic oscillator...).\end{todo} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms. On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations. The thimble projection reasoning is the one we use in Lemma~\ref{lem:thimble_proj_formula} and it is crucial for the proof of Theorem~\ref{thm:maxim}. In the Airy example (see Section~\ref{airy-appendix}) we will compute the \textit{thimble projection formula} directly.%, and by numerical check we show $\hat{\phi}\defeq\fracderiv{-1/2}{\zeta}{\alpha}\iota$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).

@@

Each term of a formal integral is an example of a {\em trans-monomial}---the basic building block of a {\em trans-series} \footnote{The full definition of a trans-series is quite involved, especially when complex exponents are allowed~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}.} The trans-monomials in the spaces $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$ are the only ones we will need to consider in the study of level-$1$ ODEs, as indicated by the Poincar\'e method~\ref{sec:Poincare method}. Then, the existence of corresponding analytic solutions is guaranteed by the Main Asymptotic Existence Theorem (M.A.E.T.). \textcolor{DarkBlue}{At the formal level, irregular singular ODEs already have distinctive behaviour. Their ``formal integral'' series solutions, discussed in Section~\ref{sec:action_transseries}, exhibit the {\em Stokes phenomenon}: asymptotic behavior that changes sharply from one direction to the next. The existence of corresponding analytic solutions is guaranteed by the Main Asymptotic Existence Theorem (M.A.E.T.).} %\textcolor{RoyalBlue}{At the formal level, irregular singular ODEs already have distinctive behaviour: they admit divergent formal series solutions in the form of trans-monomials. In particular, the trans-monomial characterizes the different asymptotic behvaiours of the underlying analytic solution---whose existence is guaranteed by the Main Asymptotic Existence Theorem (M.A.E.T.). Then, the so called Stokes phenomenon, which is also a distinguished aspect of irregular singular ODEs, measures the ``jumps" of these analytic solutions with different asymptotics, after they are analytically continued.}
\color{Maroon}
Analytic solutions of a linear ODE with an irregular singularity at $\infty$ often exhibit the Stokes phenomenon: asymptotic behavior that changes sharpy from from direction to the next. Formally, this behavior is captured in a {\em formal integral} solution: an expression
\[ \sum_{\alpha \in A} e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha \]
in which $A$ is a finite set of complex numbers, each $\sigma_\alpha$ is a real number, and each $\series{\varphi}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$. For each direction $\theta$, the term with the lowest value of $\Re(e^{i\theta} \alpha)$ represents the dominant contribution to the solution's asymptotic behavior.

@@

We can extend the definition of the Borel transform to these trans-monomials by recognizing that $\laplace_{\zeta, \alpha}$ sends ordinary monomials to trans-monomials, and then taking advantage of the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ given by identity~\eqref{change-chart}.
\begin{definition}
On each ordinary monomial within a trans-monomial, $\borel_\zeta$ acts as the formal inverse of $\laplace_{\zeta,\alpha}$:
\color{DarkBlue}
\[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-\alpha z} z^{-\nu-1} \big]=e^{-\alpha z} z^{-\nu-1}. \]
\color{DarkViolet}
\[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-\alpha z} z^{-n-1} \big]=e^{-\alpha z} z^{-n-1}. \]
The action of $\borel_\zeta$ extends to all of $e^{-\alpha z} \C\llbracket z^{-1} \rrbracket$ by countable linearity.
%The action of $\borel_\zeta$ extends to all of $e^{-\alpha z} z^\sigma\,\C\llbracket z^{-1} \rrbracket$ by countable linearity.
\end{definition}
From this definition, and identity~\eqref{change-chart}, we deduce that
\color{DarkBlue}
\begin{align*}
e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-\nu-1}\big] & = e^{-z\alpha} z^{-\nu-1} \\
\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-\nu-1}\big] & = z^{-\nu-1} \\
\borel_{\zeta}\big[e^{-z\alpha}z^{-\nu-1}\big] & = \frac{\zeta_\alpha^\nu}{\Gamma(\nu+1)}.
\end{align*}
\color{DarkViolet}
\begin{align*}
e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-n-1}\big] & = e^{-z\alpha} z^{-n-1} \\
\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-n-1}\big] & = z^{-n-1} \\
\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big] & = \frac{\zeta_\alpha^n}{n!}.
\end{align*}
\color{black}
%%%and taking the inverse of $\laplace_{\zeta_\alpha,0}$ we find
%Indeed it is possible by formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$ (see Section \ref{translation} identity \eqref{change-chart}). 
%
%We extend the Borel transform to transseries, defining \[\borel_\zeta \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta_\alpha \rrbracket\] as the formal inverse of $\laplace_{\zeta, \alpha}$. To be more precise, we define the action on trans-monomial so that the diagram
%%\begin{center}
%%\begin{tikzcd}
%%& e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \arrow[rd, "\borel_\zeta"] \\
%%\C\llbracket \zeta \rrbracket \arrow[ru, "\laplace_{\zeta, \alpha}"] \arrow[rr, "\text{change of variable}"'] & & \C\llbracket \zeta_\alpha \rrbracket
%%\end{tikzcd}
%%\end{center}
%\begin{lemma}
%%%\[\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big]=\frac{\zeta_\alpha^n}{n!}.\]
In other words, the diagram 
\begin{center}
\begin{tikzcd}[every arrow/.append style={shift left}]
\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd,"\borel_\zeta"'] \arrow[rr,"e^{-z\alpha}"]& & e^{-\alpha z} \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd, "\borel_\zeta"] \\
& & \\
\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[rr, "\mathsf{T}_{-\alpha}^*"'] & & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}\arrow[lluu,"\laplace_{\zeta_\alpha, 0}" description]\arrow{uu}{\laplace_{\zeta, \alpha}}
\end{tikzcd}
\end{center}
commutes, where $\mathsf{T}_{-\alpha}$ denotes traslation by $-\alpha$. Notice that $\laplace_{\zeta, 0}$ and $\laplace_{\zeta, \alpha}$ produce functions on the fiber $T^*_{\zeta = 0}B$, while $\laplace_{\zeta_\alpha, 0}$ produces functions on the fiber $T^*_{\zeta = \alpha}B$, so this argument depends on the fact that $z$ is defined almost globally $T^*B$.
%\end{lemma}

\color{DarkViolet}
Notice that the Borel transform extends to $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$ for $\tau\in\R\setminus\Z$ by conutably linearity. In fact, as we argue at the end of Section~\ref{sec:geometry_borel}
\[\borel_{\zeta}\big[e^{-z\alpha}z^{-\tau-1}\big] = \frac{\zeta_\alpha^\nu}{\Gamma(\tau+1)}.\]

@@

Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace \textcolor{orange}{[define $\widehat{\Omega}_\alpha$]}

@@

In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$. Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities. In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel-AL} the same.
\subsubsection{Abstract argument for Borel regularity}\label{bessel-regularity-AL}
The analysis in Sections~\ref{big-idea}\;--\;\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}. The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \singexpalg{-1/2}(\Omega_\alpha)$.
\begin{verify}
We get $v_\alpha$ from the existence result in Section~\ref{borel_reg-ODE}, which gives $v_\alpha = \zeta^{\tau_\alpha-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ \textcolor{magenta}{[What is this space? does not match notation from {\tt reg-sing-volterra}]} for some $\epsilon \in (0, 1]$. Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
\begin{align*}
v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_j^{1-\tau-\epsilon}\,v_j' \text{ is bounded near } \zeta_j = 0 \\
& \Longrightarrow \zeta_j^\epsilon\,\zeta_\alpha^{1-\tau-\epsilon}\,v_j' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
& \Longrightarrow \zeta_\alpha^{1-\tau}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
& \Longrightarrow v_\alpha' / \zeta_\alpha^{\tau_\alpha-1} \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
& \Longleftrightarrow v_j' \in o\big(\zeta_\alpha^{\tau_\alpha-1}\big).
\end{align*}
In this case, $\tau_\alpha = \tfrac{1}{2}$.
\end{verify}

@@

To confirm that the calculation above is consistent with Section~\ref{countable-cover}, use formulas \eqref{eq: K_j_mu at 1} and \eqref{eq: K_j_mu at -1} to get
\begin{align*}
K_0(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
& \hphantom{=} - \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta
\end{align*}
The hypergeometric function in the integrand can be simplified away using identity~15.4.13 from \cite{dlmf}, leaving an expression that makes the $\zeta_{\pm 1}^{1/2}$ singularities of the integrand even more apparent:
\begin{equation}\label{eqn:borel_bessel0}
K_0(z) = \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\big(\zeta^2 - 1\big)^{-1/2}\;d\zeta.
\end{equation}
We could get the same result from equation~\eqref{int:k0_cosh} by trigonometric substitution.
\begin{verify}
\par
For odd $j$, with $-\eta^2 = \tfrac{1}{2} - \tfrac{\zeta}{2}$, equation~\eqref{eq: K_j_mu at 1} gives
\begin{align*}
K^{(j)}_\mu(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} (1 + \eta^2)^{-1/2} \\
& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} \left(\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} \\
& = -\frac{1}{4} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} \\
& = -\frac{2}{4} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2}
\end{align*}
For even $j$, with $-\eta^2 = \tfrac{1}{2} + \tfrac{\zeta}{2}$, equation~\eqref{eq: K_j_mu at -1} gives
\begin{align*}
K^{(j)}_\mu(z) & = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta \\
& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} (1 + \eta^2)^{-1/2} d\zeta \\
& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} \left(\frac{1}{2} - \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \textcolor{Tomato}{i} \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{\textcolor{Tomato}{i}}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \textcolor{Tomato}{\quad\text{(?)}} \\
& = \textcolor{Tomato}{-}\frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} d\zeta \\
& = \textcolor{Tomato}{-}\frac{2 \cdot 3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
\end{align*}

>>>>

In Sections \ref{sec:geometry_laplace} and \ref{sec:geometry_borel}, we introduce a geometric picture of the Laplace and Borel transforms, generalizing the position domain from the complex plane to a translation surface $B$. Each translation chart $\zeta$ gives a different version of the Laplace transform, whose associated frequency domain is the cotangent space $T^*_{\zeta = 0} B$. The frequency coordinate $z$ is a canonical coordinate on $T^*_{\zeta = 0}B$, or on $T^*_{\zeta = 0}B^{\otimes n}$ if $\zeta = 0$ is a singularity with cone angle $2\pi n$.
\begin{center}
\phaseSpaceLaplace
\captionof{figure}{The frequency coordinate $z$ on the cotangent spaces of an ordinary point and a singular point. The singularity shown here has cone angle $6\pi$, like the singularities of the translation surface associated with the Airy function.}
\end{center}
%
\paragraph{New and old examples}
%
We illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals \textcolor{VioletRed}{[These examples are all closely related; they're not just examples of second-order ODEs]}: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}). \begin{todo}the anharmonic oscillator...).\end{todo} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms. On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations. The thimble projection reasoning is the one we use in Lemma~\ref{lem:thimble_proj_formula} and it is crucial for the proof of Theorem~\ref{thm:maxim}. In the Airy example (see Section~\ref{airy-appendix}) we will compute the \textit{thimble projection formula} directly.%, and by numerical check we show $\hat{\phi}\defeq\fracderiv{-1/2}{\zeta}{\alpha}\iota$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).

@@

Each term of a formal integral is an example of a {\em trans-monomial}---the basic building block of a {\em trans-series}.\footnote{For the full definition of a trans-series, see~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}.} The trans-monomials in the spaces $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$ are the only ones we will need to consider in the study of level-$1$ ODEs, because they are the ones used in the the Poincar\'e method, discussed in Section~\ref{sec:Poincare method}. Then, the existence of corresponding analytic solutions is guaranteed by the Main Asymptotic Existence Theorem (M.A.E.T.). \textcolor{DarkBlue}{At the formal level, irregular singular ODEs already have distinctive behaviour. Their ``formal integral'' series solutions, discussed in Section~\ref{sec:action_transseries}, exhibit the {\em Stokes phenomenon}: asymptotic behavior that changes sharply from one direction to the next. The existence of corresponding analytic solutions is guaranteed by the Main Asymptotic Existence Theorem (M.A.E.T.).} %\textcolor{RoyalBlue}{At the formal level, irregular singular ODEs already have distinctive behaviour: they admit divergent formal series solutions in the form of trans-monomials. In particular, the trans-monomial characterizes the different asymptotic behvaiours of the underlying analytic solution---whose existence is guaranteed by the Main Asymptotic Existence Theorem (M.A.E.T.). Then, the so called Stokes phenomenon, which is also a distinguished aspect of irregular singular ODEs, measures the ``jumps" of these analytic solutions with different asymptotics, after they are analytically continued.}
\color{Maroon}
Analytic solutions of a linear ODE with an irregular singularity at $\infty$ often exhibit the Stokes phenomenon: asymptotic behavior that changes sharpy from from direction to the next. Formally, this behavior is captured in a {\em formal integral} solution: an expression
\[ \sum_{\alpha \in A} e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha \]
in which $A$ is a finite set of complex numbers, each $\sigma_\alpha$ is a real number, and each $\series{\varphi}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$. For each direction $\theta$, the term with the lowest value of $\Re(e^{i\theta} \alpha)$ represents the dominant contribution to the solution's asymptotic behavior.

@@

We can extend the definition of the Borel transform to these trans-monomials by recognizing that $\laplace_{\zeta, \alpha}$ sends ordinary monomials to trans-monomials, and then taking advantage of the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ given by identity~\eqref{change-chart}.
\begin{definition}
On each ordinary monomial within a trans-monomial, $\borel_\zeta$ acts as the formal inverse of $\laplace_{\zeta,\alpha}$:
\[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-\alpha z} z^{-n-1} \big]=e^{-\alpha z} z^{-n-1}. \]
The action of $\borel_\zeta$ extends to all of $e^{-\alpha z} \C\llbracket z^{-1} \rrbracket$ by countable linearity.
\end{definition}
From this definition, and identity~\eqref{change-chart}, we deduce that
\begin{align*}
e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-n-1}\big] & = e^{-z\alpha} z^{-n-1} \\
\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-n-1}\big] & = z^{-n-1} \\
\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big] & = \frac{\zeta_\alpha^n}{n!}.
\end{align*}
%%%and taking the inverse of $\laplace_{\zeta_\alpha,0}$ we find
%Indeed it is possible by formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$ (see Section \ref{translation} identity \eqref{change-chart}). 
%
%We extend the Borel transform to transseries, defining \[\borel_\zeta \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta_\alpha \rrbracket\] as the formal inverse of $\laplace_{\zeta, \alpha}$. To be more precise, we define the action on trans-monomial so that the diagram
%%\begin{center}
%%\begin{tikzcd}
%%& e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \arrow[rd, "\borel_\zeta"] \\
%%\C\llbracket \zeta \rrbracket \arrow[ru, "\laplace_{\zeta, \alpha}"] \arrow[rr, "\text{change of variable}"'] & & \C\llbracket \zeta_\alpha \rrbracket
%%\end{tikzcd}
%%\end{center}
%\begin{lemma}
%%%\[\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big]=\frac{\zeta_\alpha^n}{n!}.\]
In other words, the diagram 
\begin{center}
\begin{tikzcd}[every arrow/.append style={shift left}]
\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd,"\borel_\zeta"'] \arrow[rr,"e^{-z\alpha}"]& & e^{-\alpha z} \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd, "\borel_\zeta"] \\
& & \\
\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[rr, "\mathsf{T}_{-\alpha}^*"'] & & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}\arrow[lluu,"\laplace_{\zeta_\alpha, 0}" description]\arrow{uu}{\laplace_{\zeta, \alpha}}
\end{tikzcd}
\end{center}
commutes, where $\mathsf{T}_{-\alpha}$ denotes traslation by $-\alpha$. Notice that $\laplace_{\zeta, 0}$ and $\laplace_{\zeta, \alpha}$ produce functions on the fiber $T^*_{\zeta = 0}B$, while $\laplace_{\zeta_\alpha, 0}$ produces functions on the fiber $T^*_{\zeta = \alpha}B$, so this argument depends on the fact that $z$ is defined almost globally $T^*B$.
%\end{lemma}

\textcolor{DarkBlue}
We can extend the Borel transform to the fractionally shifted trans-monomial spaces $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$, where $\tau \in \R \setminus \Z$, by applying the same argument to the definition at the end of Section~\ref{sec:geometry_borel}. We conclude that
\[\borel_{\zeta}\big[e^{-z\alpha}z^{-\tau-1}\big] = \frac{\zeta_\alpha^\tau}{\Gamma(\tau+1)}\]
for any $\tau \in \R\setminus\Z$.

@@

Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace

@@

In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$. Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities. In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel-AL} the same.
\subsubsection{Abstract argument for Borel regularity}\label{bessel-regularity-AL}
The analysis in Sections~\ref{big-idea}\;--\;\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}. The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \singexpalg{-1/2}(\Omega_\alpha)$.

@@

To confirm that the calculation above is consistent with Section~\ref{countable-cover}, use formulas \eqref{eq: K_j_mu at 1} and \eqref{eq: K_j_mu at -1} to get
\begin{align*}
K_0(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
& \hphantom{=} - \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta
\end{align*}
The hypergeometric function in the integrand can be simplified away using identity~15.4.13 from \cite{dlmf}, leaving an expression that makes the $\zeta_{\pm 1}^{1/2}$ singularities of the integrand even more apparent:
\begin{equation}\label{eqn:borel_bessel0}
K_0(z) = \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\big(\zeta^2 - 1\big)^{-1/2}\;d\zeta.
\end{equation}
We could get the same result from equation~\eqref{int:k0_cosh} by trigonometric substitution.
\begin{verify}
\par
For odd $j$, with $-\eta^2 = \tfrac{1}{2} - \tfrac{\zeta}{2}$, equation~\eqref{eq: K_j_mu at 1} gives
\begin{align*}
K^{(j)}_0(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} (1 + \eta^2)^{-1/2} \\
& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} \left(\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
& = -\frac{1}{4} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} d\zeta \\
& = -\frac{2}{4} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
\end{align*}
For even $j$, with $-\eta^2 = \tfrac{1}{2} + \tfrac{\zeta}{2}$, equation~\eqref{eq: K_j_mu at -1} gives
\begin{align*}
K^{(j)}_0(z) & = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta \\
& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} (1 + \eta^2)^{-1/2} d\zeta \\
& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} \left(\frac{1}{2} - \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
%%& = \color{DarkViolet}\frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left[\left(-\frac{1}{2}-\frac{\zeta}{2}\right)  \left(\frac{1}{2} - \frac{\zeta}{2}\right)\right]^{-1/2} d\zeta  \\
%%& =  \color{DarkViolet} \frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{4}+\frac{\zeta^2}{4}\right)^{-1/2} d\zeta  \\
%%& = \color{DarkViolet} \frac{2 \cdot 3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \textcolor{Tomato}{i} \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{\textcolor{Tomato}{i}}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \textcolor{Tomato}{\quad\text{(is this justified?)}} \\
& = \textcolor{Tomato}{-}\frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} d\zeta \\
& = \textcolor{Tomato}{-}\frac{2 \cdot 3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
\end{align*}
